\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
typo

We need complete feature-vector information for all stars.  For this
reason, we define the Parent Sample to be the set of all stars that
meet the \apogee\ and \gaia\ cuts and also
have the complete set of photometry: $G_n$, $\BP_n$, $\RP_n$, $J_n$,
$H_n$, $K_n$, $W_{1n}$, and $W_{2n}$ and also an apogee spectrum.
This Parent Sample contains ACE HOW MANY STARS? and is shown in \figurename~\ref{fig:parent}.
\begin{figure}
\caption{A visualization of the Parent Sample stars. The left panel
  shows a color--color diagram for all XXXX stars in the combined Parent Sample, colored by
  the \apogee\ pipeline estimates of surface gravity. The right
  panel shows small spectral segments of four example stars,
  chosen to span metallicity and surface gravity.\label{fig:parent}}
\end{figure}

>>>>

We need complete feature-vector information for all stars.  For this
reason, we define the Parent Sample to be the set of all stars that
meet the \apogee\ and \gaia\ cuts and also
have the complete set of photometry: $G_n$, $\BP_n$, $\RP_n$, $J_n$,
$H_n$, $K_n$, $W_{1n}$, and $W_{2n}$ and also an \apogee\ spectrum.
This Parent Sample contains ACE HOW MANY STARS? and is shown in \figurename~\ref{fig:parent}.
\begin{figure}
\caption{A visualization of the Parent Sample stars. The left panel
  shows a color--color diagram for all XXXX stars in the combined Parent Sample, colored by
  the \apogee\ pipeline estimates of surface gravity. The right
  panel shows small spectral segments of four example stars,
  chosen to span metallicity and surface gravity.\label{fig:parent}}
\end{figure}
